---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```
[![R-CMD-check](https://github.com/joongsup/uncmbb/workflows/R-CMD-check/badge.svg)](https://github.com/joongsup/uncmbb/actions)
[![Coverage Status](https://img.shields.io/codecov/c/github/joongsup/uncmbb/master.svg)](https://codecov.io/github/joongsup/uncmbb?branch=master)
[![CRAN status](http://www.r-pkg.org/badges/version/uncmbb)](https://cran.r-project.org/package=uncmbb)

# uncmbb

This package contains the University of North Carolina (UNC) Men's basketball team's (and their archrival Duke's) match results since 1949-1950 season with select match attributes. Base match records are obtained from the source (1) below and augmented from the source (2):

1. http://www.sports-reference.com/cbb/schools/north-carolina/
2. http://www.tarheeltimes.com/schedulebasketball-1949.aspx

Any data discrepancies are fixed once they are identified. 

## Installation

```{r cran-installation, eval = FALSE}
install.packages("uncmbb")
```

Or install the development version from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("joongsup/uncmbb")
```

## Example

```{r example}
library(uncmbb)
library(dplyr)

# Match data
tail(unc)

# NCAA championship seasons
mbb_champ_season(unc)

# Highest regular season win percentage
unc %>% mbb_season_result() %>%
        filter(Type == "REG") %>%
        arrange(desc(pct_win)) %>%
        head(5)
```
